\documentclass[a4paper,12pt]{article}
\input{preamble.tex}

% It is best practice to take brief notes of your meetings and set tasks to be completed (typically with timelines)

\title{Foucault Falcons: Meeting notes}
\date{\today}
\author{Student 1, Student 2, etc.}

\begin{document}

\maketitle

\begin{center}
\textbf{Workshop 1, November 21st}
\end{center}
\begin{itemize}
    \item Letizia Govoni, Robyn Matthews, Neha Hans attended
    \item Met for the first time, read all the materials provided by the supervisor
    \item Decided to aim to complete tasks 1-4 during Week 8 and tasks 5 and 6 in Week 9
    \item Neha will do task 1, Letizia task 2 and Robyn and Adejuwon tasks 3 and 4.
    \item Will update over whatsapp when each task is finished. Everyone should have a github account by next meeting so we can look at the code together. 
    \item note: first equation of the problem sheet shoud have -g/L instead of g/L
\end{itemize}


\begin{center}
\textbf{Meeting 1, November 26th}
\end{center}
\begin{itemize}
    \item Letizia, Robyn, Neha, Adejuwon attended 
    \item Everyone was added to a github repository and discussed translating the code into matlab
    \item next meeting on Friday
\end{itemize}
\textbf{To Do:} Everyone should finish their task by Friday, then we will start looking together on the last two tasks. 



\begin{center}
\textbf{Workshop 2, November 28th}
\end{center}
\begin{itemize}
    \item Letizia attended
    \item confirmed with the professor that the slightly wrong values in the code for task 2 are small errors caused by the calculations done on the computer
    \item task 2 is complete, we will need to decide what plots are worth putting in the report (not all of them are essential, and maybe different ones are more useful)
    \item Will update over whatsapp. Hopefully we can write a draft of the results for task 1-4 over the weekend and start working on tasks 5 and 6 next week 
    \item Talked about possibly working on task 5 and 6 together instead of having separate people working on the same thing and then compare results, this should be easy with shared codes on github. 
\end{itemize}
\textbf{To Do:} Everyone should write a draft of the results of the task they worked on.

\newpage
\begin{center}
\textbf{Meeting 2, December 3rd}
\end{center}
\begin{itemize}
    \item Neha, Robyn, Adejuwon attended
    \item worked on task 4 and 5, uploaded code to solve equation 5 (task 1)
\end{itemize}


\begin{center}
\textbf{Workshop 3, December 5th}
\end{center}
\begin{itemize}
    \item Letizia, Robyn, Neha and Adejuwon attended
    \item talked to the supervisor about the structure of the group/personal report and about how to change a plot of the angle of rotation. 
    \item 
    \item 
    \item  
    \item 
\end{itemize}




\end{document}